%% start of file `template_en.tex'.
%% Copyright 2006-1008 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper]{moderncv}

\linespread{1.2}

\usepackage{url}
\usepackage{hyperref}

% classic, casual or empty
% optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[grey]{classic}

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
\usepackage[english]{babel}
\usepackage{datetime}
\newcommand{\revision}{\twodigit\day\twodigit\month\the\year}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyfoot[RE, RO]{\footnotesize{rev. \revision}}

% adjust the page margins
\usepackage[scale=.85]{geometry}
\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
\firstname{Álex}
\familyname{González}
%\title{revisión \revision}        % optional, remove the line if not wanted
\address{c/ Miñagustín, 12, 2ºA}{37001 -- Salamanca -- Spain}    % optional, remove the line if not wanted
\mobile{(+34) 659596991}                    % optional, remove the line if not wanted
%\phone{(+34) 923995055}                      % optional, remove the line if not wanted
%\fax{fax (optional)}                          % optional, remove the line if not wanted
\email{agonzalezro@gmail.com}                      % optional, remove the line if not wanted
%\extrainfo{additional information (optional)} % optional, remove the line if not wanted
%\photo[64pt]{foto}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{\footnotesize{
%    access, \textbf{ajax}, \textbf{android}, apache,
%    bash scripting,
%    \textbf{c}, \textbf{c++}, corel draw, \textbf{css}, cyrus,
%    div, \textbf{django}, dns,
%    firewall, flash, freebsd,
%    gimp, \textbf{git}, \textbf{gtk}, gtkmozembed,
%    hotspot, html,
%    inkscape, iphone,
%    \LaTeX,
%    \textbf{java}, j2me, \textbf{javascript},
%    \textbf{linux},
%    melsec medoc, \textbf{mercurial}, mojo, mysql,
%    openoffice, osx, photoshop,
%    \textbf{php}, pygtk, \textbf{python},
%    \textbf{rest},
%    samba, squid, squirrelmail, subversion,
%    visual basic,
%    webkit, windos mobile, windows\ldots
%}}

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page

%FIX footnote problems
\makeatletter\newcommand\@makefntext[1]{\parindent 1em\noindent\hb@xt@1.8em{\hss\@makefnmark}#1}\makeatother

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Areas of interest}
\cvline{}{Web development (backend \& frontend), APIs development \& consumption, mobile \hyphenation{development}development, usability, geopositioning, augmented reality and consulting.}

\section{Professional experience}
\cventry{Apr 2010--Cur.}{Technology responsible}{lukkom}{}{}{Web platform and REST API development, management consulting and secondary IT works.}

\cventry{Mar 2009--Apr 2010}{Founder}{mirblu S.L.}{}{}{Development in several languages: Python, PHP, Java, Bash Scripting and Visual Basic. Customer search. Business administration works.}

\cventry{2007--2009}{Movente scholar}{Pontifical University of Salamanca (Spain) and Caja Duero Foundation\footnotemark}{}{}{Development and research of a BPS (bluetooth position system) with path calculation between two points in a building. Part of a project for mobile platform developed with J2ME.}
%full%\footnotetext{Dr. Encarna Beato,  Movente projects coordinator. \href{mailto://ebeatogu@upsa.es}{\texttt{$<$ebeatogu@upsa.es$>$}}} 

\cventry{2008--2009, 2005--2007}{Classroom scholar}{Pontifical University of Salamanca (Spain)\footnotemark}{}{}{Responsible for the proper use of UPSA computer rooms.\\Net laboratory scholar, installation and configuration of a new server.}
%full%\footnotetext{Dr. Mariano Raboso, Collaboration scholars coordinator. \href{mailto://mrabosoma@upsa.es}{\texttt{$<$mrabosoma@upsa.es$>$}}}

\cventry{2008 (1 month)}{Teacher}{PC Carrier\footnotemark}{}{}{Relational databases teacher OpenOffice.org to ``Xunta de Galicia''.}
%full%\footnotetext{Sonia Sainz, teachers coordinator. \href{mailto://soniasainz@pcarrier.com}{\texttt{$<$soniasainz@pcarrier.com$>$}}}

\cventry{2007--2008}{Tecnoduero scholar}{Caja Duero Foundation}{}{}{Teacher and technical support to digital literacy of disadvantaged groups.}

\cventry{2007 (2 months)}{Campus Fórmate virtual classroom technical responsible and technical support to the classroom teaching infrastructure}{Matchmind S.L.\footnotemark}{}{}{Moodle LMS administrator: administration of classroom contents and custom adaptations (PHP \& CSS). \\ Servers installation and configuration: Apache Tomcat, Subversion, exim4 with clamav, spamassasin, SquirrelMail, Iptables, Squid\ldots}
%full%\footnotetext{D. Arturo Pérez, training unit manager. \href{mailto://arperez@matchmind.es}{\texttt{$<$arperez@matchmind.es$>$}}}

%full%\cventry{2006 (2 months)}{Teacher}{Academia Universitaria}{}{}{Teacher of C programming language for statistics students.}

\cventry{2004 (3 months)}{Technical practices}{Regox, servicios informáticos}{}{}{Administration business server (regox.net \& tesdai.com), design of advertisement, equipment assembly, network cabling\ldots}


\section{Education}
\subsection{Academic}
%\cventry{year--year}{Degree}{Institution}{City}{\textit{Grade}}{Description}
\cventry{2009--Cur.}{MSc Electronic Commerce}{University of Salamanca (Spain)}{}{}{}
\cventry{2004--2009}{BSc Computer Science}{Pontifical University of Salamanca (Spain)}{}{}{}
\cventry{2002--2004}{Higher level vocational training at computer systems management}{Tesdai}{}{}{}

\subsection{Non academic}
\cventry{2010--Cur.}{Professional certification in architecture of digital content applications}{University of Salamanca (Spain)}{}{}{}
\cventry{Feb 2009}{iPhone development}{Pontifical University of Salamanca (Spain)}{}{}{}
\cventry{Feb 2009}{Android development}{Pontifical University of Salamanca (Spain)}{}{}{}
\cventry{Dec 2009}{Windows Mobile development}{Pontifical University of Salamanca (Spain)}{}{}{}
\cventry{Jan 2008}{J2ME development}{Pontifical University of Salamanca (Spain)}{}{}{}
%full%\cventry{Dec 2007}{Messaging and location with Java (Tempos21 platform)}{Pontifical University of Salamanca (Spain)}{}{}{}
%full%\cventry{Nov 2007}{Java foundations}{Pontifical University of Salamanca (Spain)}{}{}{}
\cventry{2008 (2 months)}{Apache2 management}{Germán Sánchez Ruiperez Foundation}{}{}{}
\cventry{2007 (2 months)}{PHP5 advanced development}{Germán Sánchez Ruiperez Foundation}{}{}{}
\cventry{2004 (2 months)}{GNU/Linux security technical}{Tesdai}{}{}{}

\section{Technologies}
\cvline{}{
    \textbf{ajax}, \textbf{android}, apache,
    bash scripting,
    \textbf{c}, \textbf{c++}, corel draw, \textbf{css}, cyrus,
    \textbf{django}, dns,
    firewall, flash, freebsd,
    gimp, \textbf{git}, \textbf{gtk}, gtkmozembed,
    hotspot, html,
    inkscape, iphone,
    \LaTeX, \textbf{linux},
    \textbf{java}, j2me, \textbf{javascript},
    \textbf{linux},
    \textbf{mercurial}, mojo, mysql,
    openoffice,
    \textbf{php}, pygtk, \textbf{python},
    \textbf{rest},
    samba, squid, squirrelmail, subversion,
    visual basic,
    webkit, windos mobile\ldots
}

\section{Languages}
\cvlanguage{Galician}{\hbox{Mother tongue.}}{}
\cvlanguage{Spanish}{\hbox{Mother tongue.}}{}
\cvlanguage{English}{\hbox{Good reading. Good writing. Medium speaking.}}{}
\cvlanguage{Portuguese}{\hbox{Understanding level.}}{}


\section{Other interesting information}
\cvline{1}{The BPS was selected as one of the best I+D project of Castilla y León by the Fundación Universidades.}
\cvline{2}{Speaker in several business and technical talks. As an example: JME talk at Xuventude Galiza Net '09, to I+D+i managers at \hyphenation{ADEuropa}ADEuropa, or about FLOSS with CENATIC.}
\cvline{3}{Developer of the CMS that people used at \url{rianxosencabos.com}, \url{sanciprian.com} and \url{alex.rianxosencabos.com}.}
\cvline{4}{My last public repository at \url{github.com/agonzalezro}.}
\cvline{5}{Active participant in several associations: AGNIX, RSC, GALPon.}

%\section{Tags}
%\cvlistitem[]{python, django, php, mysql, html, c, c++, div, visual basic, bash scripting, j2me, j2se, javascript, android, windos mobile, iphone, melsec medoc, inkscape, gimp, corel draw, photoshop, flash, linux, windows, osx, freebsd, access, openoffice, hotspot, dns, firewall, samba, squid, apache, cyrus, squirrelmail, gtk, pygtk, gtkmozembed, mojo, webkit\ldots}

\end{document}
